# Section 1 

## Research questions 

::::: columns

::: {.column width="50%"}
- **Tracing Educational Pathways in Europe: Transmission from Mothers and Fathers**
  - We created a plot function (plot_sankey) that generates Sankey plots to show the pathway from mother/father to child.
  - The plot_sankey function can be easily reused to show other pathways.
  - Data source: European Social Survey 4-11.
  - Measure: International Standard Classification of Education (ISCED)
:::

::: {.column width="50%"}
- **Mapping Intergenerational Transmission of Educational (dis)advantage across Europe**
  - We created a plot function (plot_map) that generates maps to show variations in mother/father-child correlation across Europe.
  - The plot_map function can be easily reused for mapping variations of other variables across Europe.
  - Data source: European Social Survey 4-11.
  - Measure: Correlation between children's ISCED and mother/father's ISCED by country
:::

:::::

# Section 2 

```{r setup, include=FALSE}
source("../visualization/01_select_dataset.R")
source("../visualization/02_select_variable.R")
source("../visualization/03_read_data.R")
source("../visualization/06_prepare_sankey.R")
source("../visualization/07_prepare_map.R")
```

## Tracing Educational Pathways in Europe: Transmission from Mothers and Fathers

```{r}
#| label: fig-figure1
#| fig-cap: "Mother-to-child Educational Pathway (left to right)"
#| fig-align: center
#| echo: false

p1
```

```{r}
#| label: fig-figure2
#| fig-cap: "Father-to-child Educational Pathway (left to right)"
#| fig-align: center
#| echo: false

p2
```

## Mapping Intergenerational Transmission of Educational (dis)advantage across Europe

```{r}
#| label: fig-figure3
#| fig-cap: "Intergenerational Transmission of Educational (Dis)advantage across Europe: Mother-Child Correlation"
#| fig-align: center
#| echo: false

p3
```

```{r}
#| label: fig-figure4
#| fig-cap: "Intergenerational Transmission of Educational (Dis)advantage across Europe: Father-Child Correlation"
#| fig-align: center
#| echo: false

p4
```

## R packages 

In this project, we used R packages in R version 4.4.2 via RStudio to perform data visualization. The specific versions of these packages, along with their dependencies, are captured in the renv.lock file.

## Data source
ESS Round 11: European Social Survey European Research Infrastructure (ESS ERIC) (2024) ESS11 - integrated file, edition 2.0 [Data set]. Sikt - Norwegian Agency for Shared Services in Education and Research. https://doi.org/10.21338/ess11e02_0.

ESS Round 10: European Social Survey Round 10 Data (2020). Data file edition 3.0. Sikt - Norwegian Agency for Shared Services in Education and Research, Norway – Data Archive and distributor of ESS data for ESS ERIC. doi:10.21338/NSD-ESS10-2020.

ESS Round 9: European Social Survey Round 9 Data (2018). Data file edition 3.1. Sikt - Norwegian Agency for Shared Services in Education and Research, Norway – Data Archive and distributor of ESS data for ESS ERIC. doi:10.21338/NSD-ESS9-2018.

ESS Round 8: European Social Survey Round 8 Data (2016). Data file edition 2.2. Sikt - Norwegian Agency for Shared Services in Education and Research, Norway – Data Archive and distributor of ESS data for ESS ERIC. doi:10.21338/NSD-ESS8-2016.

ESS Round 7: European Social Survey Round 7 Data (2014). Data file edition 2.2. Sikt - Norwegian Agency for Shared Services in Education and Research, Norway – Data Archive and distributor of ESS data for ESS ERIC. doi:10.21338/NSD-ESS7-2014.

ESS Round 6: European Social Survey Round 6 Data (2012). Data file edition 2.4. Sikt - Norwegian Agency for Shared Services in Education and Research, Norway – Data Archive and distributor of ESS data for ESS ERIC. doi:10.21338/NSD-ESS6-2012.

ESS Round 5: European Social Survey Round 5 Data (2010). Data file edition 3.4. Sikt - Norwegian Agency for Shared Services in Education and Research, Norway – Data Archive and distributor of ESS data for ESS ERIC. doi:10.21338/NSD-ESS5-2010.

ESS Round 4: European Social Survey Round 4 Data (2008). Data file edition 4.5. Sikt - Norwegian Agency for Shared Services in Education and Research, Norway – Data Archive and distributor of ESS data for ESS ERIC. doi:10.21338/NSD-ESS4-2008.

